DOpElib: Differential Equations\\ and Optimization Environment

### 2013-07-23 Examples/PDE/StatPDE/Example12/content.tex
Typo removed

Most things are identical to all the other programs. However there is a subtle difference in 
\texttt{localpde.h}: Although the element used has 3 components (two for the RT-Element and 1 for the pressure)
the block_component vector mapping blocks to components has only 2 entries. 1 for each finite element used!

>>>>

Most things are identical to all the other programs. However there is a subtle difference in 
\texttt{localpde.h}: Although the element used has 3 components (two for the RT-Element and 1 for the pressure)
the block\underline{ }component vector mapping blocks to components has only 2 entries. 1 for each finite element used!
